Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-21 documentation/paper.tex
Added footnotes for authors
Addressed more comments

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{lineno}
\linenumbers

\renewcommand*{\Affilfont}{\footnotesize}

@@

    \begin{enumerate}
        \item Neutron calibration sets, which are known to contain approximately 90\% neutrons, and
        \item WIMP search runs, which contain approximately 99\% alpha particles
    \end{enumerate}
\end{enumerate}

@@

The detector was filled with 52 kg of liquid C$_3$F$_8$, which was held at a constant temperature by a large chilled water bath. The pressure of the target liquid, held inside a synthetic quartz inner vessel, was precisely accurately controlled with propylene glycol as hydraulic fluid inside a stainless steel pressure vessel (Figure \ref{pico_cad}).

@@

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{lineno}

\linenumbers

\renewcommand*{\Affilfont}{\footnotesize}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

@@

    \begin{enumerate}
        \item Neutron calibration sets, which are known to contain approximately 90\% neutrons, and
        \item Previously blinded WIMP search runs and diagnostic background runs, which contain approximately 99\% alpha particles.
    \end{enumerate}
\end{enumerate}

@@

The detector was filled with 52 kg of liquid C$_3$F$_8$, which was held at a constant temperature by a large chilled water bath. The pressure of the target liquid, held inside a synthetic quartz inner vessel, was precisely controlled with propylene glycol as hydraulic fluid inside a stainless steel pressure vessel (Figure \ref{pico_cad}).

@@

(Note that in Figure \ref{grav_grid_search}, AP is normalized differently than in the original PICO-60 study. In this normalized spectrum, the decision boundary between neutrons and alpha particles is at 0.25.)
